### 2017-05-02 paper/evaluation.tex
speedups
updated RQ6

It is important to note that we under-estimated cost in our
experiments for two main reasons.  First, some tests may finish
earlier than expected due to observed test failures in some of the
revisions we downloaded.  From the \numSubjs{} testable projects,
\numSubjsPass{} successfully executed all tests and \numSubjsFail{}
reported some test failures.  Second, some projects may omit
long-running tests on their default execution. For instance, the
project \CodeIn{apache.maven-surefire} runs all unit tests in a few
seconds.  According to our criteria, this project is to be classified
as \shortg{} but a closer look reveals that only smoke tests are run
by default in this project.  Time-consuming integration and system
tests are only accessible via custom parameters, which we do not
handle in our experimental setup.  We enabled such parameters for this
specific project and observed that testing time goes to nearly 30
minutes.  For simplicity, we considered only the tests executed by
default.

@@

To answer this research question, we considered all six parallel
levels from Section~\ref{sec:modes} and we selected the top 10
projects with long-running tests suites that satisfies the following
criteria: (1) tests run in sequence by default and (2) test suite
consists only by passing tests. The first criteria is to use the
default execution (\ie, configuration \Seq{}) as a baseline to compare
speedup with the other parallel configurations. The second criteria is
to avoid introducing noise when measuring the rate of flakiness caused
by the non-deterministic execution of tests. We are interested only in
failures manifested when parallelism is enabled. Since the number of
failing tests may vary, we run each project three times and report the
average elapsed time and rate of flakiness.
Figures~\ref{tab:rq6-efficiency} (ordered by time cost)
and~\ref{tab:rq6-flaky} (ordered by the number of tests) summarize the
obtained results.

\begin{figure}[h!]
\centering
\resizebox{.48\textwidth}{!}{%
\begin{tabular}{lrrrrrr}
\toprule
\emph{Subject} & \emph{\Seq{}} & \emph{\SeqClassParMeth{}} & \emph{\ParClassSeqMeth{}} & \emph{\ParClassParMeth{}} & \emph{\ForkSeq{}} & \emph{\ForkParMeth{}}\\%
\midrule%
%% Linkedin Pinot & 3480.091s & 1703.958s & 24.726s & 2229.822s & 783.12s & 761.973s\\%
%% Linkedin Pinot & 58m & 2.04x & 140x & 1.56x & 4.44x & 4.56x\\%
%% Jenkins CI Github Plugin & 3298.603s & 2049.709s & 1547.261s & 1240.544s & 2975.232s & 227.214s \\%
%% Jenkins CI Github Plugin & 55m & 1.60x & 2.13x & 2.65x & 1.10x & 14.51x \\%
%% Kite SDK & - & - & - & - & - & -\\%
%% Apache Giraph & 1041.884s & 37.666s & 116.78s & 1037.105s & 1038.39s & 45.992s\\%
%% \Fix{!?} Apache Giraph & 17.36m & 27.66x & 8.92x & 1.00x & 1.00x & 22.65x\\%
%% OpenMRS Core & - & - & - & - & - & -\\%
%% Jenkins CI Docker Workflow Plugin & 447.069s & 490.675s & 27.69s & 8.244s & 439.207s & 38.3s\\%
%% Jenkins CI Docker Workflow Plugin & 7.45m & 0.91x & 16.14x & 54.22x & 1.01x & 11.67x\\%
%% \Fix{Flaky} Apache Eagle & - & - & - & - & - & -\\%
Geotools & 8.41m & - & - & - & - & -\\%
Atomix & 7.78m & - & - & - & - & -\\%
Kuromoji & 7.68m & - & - & - & - & -\\%
%%\Fix{Snazy OHC} & - & - & - & - & - & -\\%
%%\Fix{RoaringBitmap} & - & - & - & - & - & -\\%
\bottomrule%
\end{tabular}}
\caption{\Fix{Tabela de eficiencia}}
\label{tab:rq6-efficiency}
\end{figure}

@@

\begin{figure}[h!]
\centering
\resizebox{.48\textwidth}{!}{%
\begin{tabular}{lcrrrrr}
\toprule
\emph{Subject} & \emph{\# of tests} & \emph{\SeqClassParMeth{}} & \emph{\ParClassSeqMeth{}} & \emph{\ParClassParMeth{}} & \emph{\ForkSeq{}} & \emph{\ForkParMeth{}}\\%
\midrule%
%% Linkedin Pinot & 664 & - & - & - & - & -\\%
%% Jenkins CI Github Plugin & - & - & - & - & 0\% & -\\%
%% Kite SDK & - & - & - & - & - & -\\%
%% \Fix{!?} Apache Giraph & 327 & - & - & - & - & -\\%
%% OpenMRS Core & - & - & - & - & - & -\\%
%% Jenkins CI Docker Workflow Plugin & - & - & - & - & 0\% & -\\%
%% \Fix{Flaky} Apache Eagle & - & - & - & - & - & -\\%
Geotools & 7701 & - & - & - & - & -\\%
Kuromoji & 672 & - & - & - & - & -\\%
Atomix & 99 & - & - & - & - & -\\%
%%\Fix{Snazy OHC} & - & - & - & - & - & -\\%
%%\Fix{RoaringBitmap} & - & - & - & - & - & -\\%
\bottomrule%
\end{tabular}}
\caption{\Fix{Tabela de flakiness}}
\label{tab:rq6-flaky}
\end{figure}

@@

\Fix{Conclude}

@@

\Fix{Jean and Luis should write this. This is really important for an
  empirical study.  You need to undertand main sources of threat:
  internal, external, and construct.  Read this document for the
  basics: http://www.statsdirect.com/help/basics/validity.htm.  Read
  this document for an example:
  http://www.cin.ufpe.br/~damorim/publications/perez-etal-icst2017.pdf}

>>>>

It is important to note that we under-estimated cost in our
experiments for two main reasons.  First, some tests may finish
earlier than expected due to the observed test failures in some of the
revisions we downloaded.  From the \numSubjs{} testable projects,
\numSubjsPass{} successfully executed all tests and \numSubjsFail{}
reported some test failures.  Second, some projects may omit
long-running tests on their default execution. For instance, the
project \CodeIn{apache.maven-surefire} runs all unit tests in a few
seconds.  According to our criteria, this project is to be classified
as \shortg{} but a closer look reveals that only smoke tests are run
by default in this project.  Time-consuming integration and system
tests are only accessible via custom parameters, which we do not
handle in our experimental setup.  We enabled such parameters for this
specific project and observed that testing time goes to nearly 30
minutes.  For simplicity, we considered only the tests executed by
default.

@@

%% The intuition is that efficiency and flakiness are inversely
%% proportional in some cases: if too many tests depends on the state of
%% a single external resource, several tests are likely to fail as the
%% degree of concurrency increases by exploiting maximum CPU usage.

To answer this research question, we conducted an experiment involving
the six parallel levels from Section~\ref{sec:modes}  and the top 10
projects with long-running tests suites from our sample set. We are
interested in understanding how efficiency (\ie, testing cost) and
flakiness (\ie, failing tests) are affected when we run a test suite
with different parallel levels. \Jbc{I think we must have a sentence
to motivate why we want to understand this relationship}.  We used as
a \emph{control group} (\ie, baseline) the sequential execution of
each subject's tests. Notice that for measuring flakiness, we have to
consider only tests that failed due to the concurrency in the parallel
execution. To this purpose, we re-executed the tests in sequence ten
times and carefully verified that there are only passing tests in our
baseline. We considered ten as the number of re-executions based on
the approach used by Google reported in a previous work on test
flakiness~\cite{luo-etal-fse2014}. For the parallelism configurations,
we implemented a script that takes a subject and a configuration
(\eg, \ForkSeq{}) as inputs, and the script outputs the modified
version of the subject with the desired configuration. The workflow
consists in copying the project directory to a new directory, finding
all existing build files (\ie, \pomf{} files), and modifying all
existing Maven Surefire configurations with new values for the
parameters \CodeIn{parallel}, \CodeIn{forkCount}, and
\CodeIn{threadCount} using an XPath~\cite{xpath} library to manipulate
XML documents. For configurations with forked JVMs enabled (\ie,
\ForkSeq{} and \ForkParMeth{}), we changed the \CodeIn{forkCount} with
the value \CodeIn{1C} (\ie, one JVM per core). To adjust the pool of
threads for parallelism within a JVM, we changed the parameter
\CodeIn{threadCount} with \Jbc{should we consider 2 as it is the
number of native threads per core OR 6 as it represents 3 Cores * 2
native threads?}.  To run the subjects and their respective variations
(\ie, the modified versions according to the parallelism
configuration), we used a similar approach as in
Figure~\ref{fig:mvn-execution} except that we added a timeout of one
hour to run the tests. We used the \CodeIn{timeout}
command~\cite{timeout-cmd} to monitor the execution, and we configured
the command to dispatch a \emph{kill} signal if the test execution
exceeds the time limit. We imposed this time constraint to avoid
hanging indefinitely the experiment execution due to some thread
contention that may occur (\eg, deadlock). Finally, we saved each
execution log and XML test reports generated by Maven to collect the
execution time, the number of failing tests, and for reference to
analyze and diagnose outliers in our results. For efficiency, we
reported the speedup (\ie, $T_{\text{sequence}} /
T_{\text{parallel}}$) in average, and for flakiness, we reported the
rate of failing tests (\ie, $failures / tests$) in average.
Figure~\ref{tab:rq6-table} (ordered by time cost) summarizes the
obtained results.

%% that satisfies the following criteria: (1) tests run in sequence by
%% default and (2) test suite consists only by passing tests. The first
%% criteria is to use the default execution (\ie, configuration \Seq{})
%% as a baseline to compare speedup with the other parallel
%% configurations. The second criteria is to avoid introducing noise when
%% measuring the rate of flakiness caused by the non-deterministic
%% execution of tests. We are interested only in failures manifested when
%% parallelism is enabled. Since the number of failing tests may vary, we
%% run each project three times and report the average elapsed time and
%% rate of flakiness.

%% Table header macros
\newcommand{\subcolA}{$\Uparrow_\text{speed}$}
\newcommand{\subcolB}{$\%_\text{fail}$}
\newcommand{\colheader}[1]{\multicolumn{2}{c|}{\emph{#1}}}
\newcommand{\subcol}{\subcolA{} & \subcolB{}}
\newcommand{\entry}[2]{#1x & #2\%}

\begin{figure*}[t]
\centering
\begin{tabular}{|l|r|rr|rr|rr|rr|rr|}
\hline%

\multirow{2}{*}{\emph{Subject}} & \emph{\Seq{}} &
    \colheader{\SeqClassParMeth} & \colheader{\ParClassSeqMeth} &
    \colheader{\ParClassParMeth} & \colheader{\ForkSeq} &
    \colheader{\ForkParMeth} \\ \cline{2-12}
    & $T_\text{cost}$ & \subcol{} & \subcol{} & \subcol{} & \subcol{}
    & \subcol{}\\%

\hline%
Subject A & Xm & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B}\\%
Subject A & Xm & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B}\\%
Subject A & Xm & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B}\\%
Subject A & Xm & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B}\\%
Subject A & Xm & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B}\\%
Subject A & Xm & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B}\\%
Subject A & Xm & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B}\\%
Subject A & Xm & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B}\\%
Subject A & Xm & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B}\\%
Subject A & Xm & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B}\\%

%% Linkedin Pinot & 3480.091s & 1703.958s & 24.726s & 2229.822s & 783.12s & 761.973s\\%
%% Linkedin Pinot & 58m & 2.04x & 140x & 1.56x & 4.44x & 4.56x\\%
%% Jenkins CI Github Plugin & 3298.603s & 2049.709s & 1547.261s & 1240.544s & 2975.232s & 227.214s \\%
%% Jenkins CI Github Plugin & 55m & 1.60x & 2.13x & 2.65x & 1.10x & 14.51x \\%
%% Kite SDK & - & - & - & - & - & -\\%
%% Apache Giraph & 1041.884s & 37.666s & 116.78s & 1037.105s & 1038.39s & 45.992s\\%
%% Apache Giraph & 17.36m & 27.66x & 8.92x & 1.00x & 1.00x & 22.65x\\%
%% OpenMRS Core & - & - & - & - & - & -\\%
%% Jenkins CI Docker Workflow Plugin & 447.069s & 490.675s & 27.69s & 8.244s & 439.207s & 38.3s\\%
%% Jenkins CI Docker Workflow Plugin & 7.45m & 0.91x & 16.14x & 54.22x & 1.01x & 11.67x\\%
%% \Fix{Flaky} Apache Eagle & - & - & - & - & - & -\\%
%% Geotools & 8.41m & - & - & - & - & -\\%
%% Atomix & 7.78m & - & - & - & - & -\\%
%% Kuromoji & 7.68m & - & - & - & - & -\\%
%%\Fix{Snazy OHC} & - & - & - & - & - & -\\%
%%\Fix{RoaringBitmap} & - & - & - & - & - & -\\%

\hline%
\end{tabular}
\caption{\Fix{Tabela de eficiencia e flakiness}}
\label{tab:rq6-table}
\end{figure*}

%% \begin{figure}[h!]
%% \centering
%% \resizebox{.48\textwidth}{!}{%
%% \begin{tabular}{lcrrrrr}
%% \toprule
%% \emph{Subject} & \emph{\# of tests} & \emph{\SeqClassParMeth{}} & \emph{\ParClassSeqMeth{}} & \emph{\ParClassParMeth{}} & \emph{\ForkSeq{}} & \emph{\ForkParMeth{}}\\%
%% \midrule%
%% Linkedin Pinot & 356 & - & - & - & - & -\\%
%% %% Jenkins CI Github Plugin & - & - & - & - & 0\% & -\\%
%% %% Kite SDK & - & - & - & - & - & -\\%
%% %% \Fix{!?} Apache Giraph & 327 & - & - & - & - & -\\%
%% %% OpenMRS Core & - & - & - & - & - & -\\%
%% %% Jenkins CI Docker Workflow Plugin & - & - & - & - & 0\% & -\\%
%% %% \Fix{Flaky} Apache Eagle & - & - & - & - & - & -\\%
%% %%Geotools & 7701 & - & - & - & - & -\\%
%% %%Kuromoji & 672 & - & - & - & - & -\\%
%% %%Atomix & 99 & - & - & - & - & -\\%
%% %%\Fix{Snazy OHC} & - & - & - & - & - & -\\%
%% %%\Fix{RoaringBitmap} & - & - & - & - & - & -\\%
%% \bottomrule%
%% \end{tabular}}
%% \caption{\Fix{Tabela de flakiness}}
%% \label{tab:rq6-flaky}
%% \end{figure}

@@

@@

\Fix{highlight special cases}

\Fix{Draw conclusions}

@@

\Fix{To appear... Elaborate CONSTRUCT, INTERNAL and EXTERNAL threats.
I'm going to be writing this ASAP as I finish to present the results
from RQ6}
